### 2020-03-04 README.Rmd
Working on the readme and some changes to package.

bw_growth_df <- 
  # Merge both censuses and compute growth:
  compute_growth(census_df1, census_df2, id) %>% 
  mutate(sp = to_any_case(sp)) %>% 
  left_join(bw_species, by = c("sp" = "spcode"))
```

@@

# ID which points are in buffer and which are not
index <- st_intersects(bw_growth_df, bw_buffer, sparse = FALSE)
bw_growth_df <- bw_growth_df %>% 
  mutate(buffer = index)

@@

# ID which points are in buffer and which are not
index <- st_intersects(scbi_growth_df, scbi_buffer, sparse = FALSE)
scbi_growth_df <- scbi_growth_df %>% 
  mutate(buffer = index)

@@

* `model_number = 1`: No competition growth only depends on `dbh` and individual grouping.
* `model_number = 2`: Competition but identity of competitor does not matter, just sum of competitior biomass.
* `model_number = 3`: Full model with competition and competitor identity.

@@

* `get_model_specs()`. Inputs:
    + define identification/grouping classification
    + `growth_df` format
* `create_focal_and_comp()`. Inputs:
    + `growth_df`
    + `max_dist`: who are your competitors
    + `model_specs`: grouping of competitor biomasses

>>>>

bw_growth_df <- 
  # Merge both censuses and compute growth:
  compute_growth(census_df1, census_df2, id) %>% 
  mutate(sp = to_any_case(sp))
```

@@

# ID which points are in buffer and which are not
index <- st_intersects(bw_growth_df, bw_buffer, sparse = FALSE)
bw_growth_df <- bw_growth_df %>% 
  mutate(buffer = index[,1])

@@

# ID which points are in buffer and which are not
index <- st_intersects(scbi_growth_df, scbi_buffer, sparse = FALSE)
scbi_growth_df <- scbi_growth_df %>% 
  mutate(buffer = index[,1])

@@

* `model_number = 1`: No competition growth only depends on focal tree `dbh` and grouping.
* `model_number = 2`: Competition but identity of competitor does not matter, just sum of competitior basal area.
* `model_number = 3`: Full model with competition including competitor identity.

@@

Next we create the `focal_vs_comp` object which connects each tree to the trees in its competitive neighborhood (with `max_dist`). This required `growth_df`, `max_dist`, `cv_fold_size`, and `model_specs` as inputs.

```{r}
bw_focal_vs_comp <- create_focal_vs_comp(bw_growth_df, max_dist, cv_fold_size, bw_specs)
scbi_focal_vs_comp <- create_focal_vs_comp(scbi_growth_df, max_dist, cv_fold_size, scbi_specs)
